Enuri Dissanayake

### 2023-09-23 team/junior/enuri-dissanayake.qmd
fix typo

---
title: "Enuri Dissanayake"
subtitle: "Undergraduate thesis student"
image: enuri-dissanayake.jpg
sortby: 5
started: "September 2023"
about:
  id: hero-heading
  template: solana
---

>>>>

---
title: "Enuri Dissanayake"
subtitle: "Undergraduate practicum student"
image: enuri-dissanayake.jpg
sortby: 5
started: "September 2023"
about:
  id: hero-heading
  template: solana
---
